Estimating duration in the presence of misclassification

### 2024-01-23 transmission.tex
section/chapter consistent usage

    \node[draw, thick, inner sep=0.3cm, fit=(P1) (P3), fill=blue!10,opacity=0.2] {};
\end{tikzpicture}
}
  \caption[SEIR model]{SEIR model used for the analysis in this chapter. The shaded box represents PCR-positive individuals. Shown for a single stratum.}
  \label{SEIR:fig:full-model}
\end{figure}

@@

The results in this chapter show the feasibility of fitting a mechanistic model using only data on prevalence.
If the distributions for length-of-stay in each compartment are known, then all other model parameters can  be estimated.
This includes the age distribution of the infections and the susceptibility of children.

>>>>

    \node[draw, thick, inner sep=0.3cm, fit=(P1) (P3), fill=blue!10,opacity=0.2] {};
\end{tikzpicture}
}
  \caption[SEIR model]{SEIR model used for the analysis in this section. The shaded box represents PCR-positive individuals. Shown for a single stratum.}
  \label{SEIR:fig:full-model}
\end{figure}

@@

The results in this section show the feasibility of fitting a mechanistic model using only data on prevalence.
If the distributions for length-of-stay in each compartment are known, then all other model parameters can  be estimated.
This includes the age distribution of the infections and the susceptibility of children.
